CommonMind Consortium: DLPFC

### 2020-09-17 combined_analysis/diff.networks.Rmd
Update diff networks

```{r modules.in.second.cohort.Dx, fig.width=8, fig.height=100}

@@

>>>>

```{r modules.in.second.cohort.Dx, fig.width=15, fig.height=100}

@@

X = matrnorm(300, 1000)

C_x = cor(X)

C = C_x[1:5, 1:5]
colnames(C) = paste0('gene_', 1:5)
rownames(C) = colnames(C)

library(ggraph)
library(ggplot2)
library(tidygraph)
library(Rfast)

load("~/Downloads/C.test.RDATA")

C = C1 - C2

plot_corr_network( C1-C2 )

rstat_nodes <- data.frame(name = c("H

	adley", "David", "Romain", "Julia"))
rstat_edges <- data.frame(from = c(1, 1, 1, 2, 3, 3, 4, 4, 4),
                         to = c(2, 3, 4, 1, 1, 2, 1, 2, 3))
rstat_edges$weight = 1:9

rstat_nodes <- data.frame(name = c("Hadley", "David", "Romain", "Julia"))
rstat_edges <- data.frame(from = c(1, 1, 1, 2, 3, 3, 4, 4, 4),
                         to = c(2, 3, 4, 1, 1, 2, 1, 2, 3))
rstat_edges$weight = 1:9

net = tbl_graph(nodes = rstat_nodes, edges = rstat_edges, directed=FALSE)

ggraph(net, layout = "auto") + 
  geom_node_point(size=10, color="blue") +
  geom_edge_link(aes(width = weight), alpha = 0.8) + 
  scale_edge_width(range = c(0.2, 2)) +
  geom_node_text(aes(label = name), repel = TRUE) +
  labs(edge_width = "Correlation") +
  theme_graph()

net = ggnetwork(C)

set.edge.attribute
set.edge.value

ggplot(net, aes(x = x, y = y, xend = xend, yend = yend)) + theme_blank() + geom_nodes(aes(x,y)) + geom_edges()

ggplot(
ggnetwork(emon[[1]], layout = "kamadakawai", arrow.gap = 0.025),
aes(x, y, xend = xend, yend = yend) )+
geom_edges(aes(color = Frequency, size=Frequency^2),
arrow = arrow(length = unit(10, "pt"), type = "closed")
)+
geom_nodes(aes(size = Formalization)) + scale_color_gradient(low = "grey50", high = "tomato") + scale_size_area(breaks = 1:3) +
theme_blank()

net = network(C)

get.edges(net, "gene_1")

rstat_nodes <- data.frame(name = c("Hadley", "David", "Romain", "Julia"))
rstat_edges <- data.frame(from = c(1, 1, 1, 2, 3, 3, 4, 4, 4),
                         to = c(2, 3, 4, 1, 1, 2, 1, 2, 3))
rstat_edges$weight = 1:9

net = tbl_graph(nodes = rstat_nodes, edges = rstat_edges, directed=FALSE)

ggraph(net, layout = "auto") + 
  geom_node_point(size=10, color="blue") +
  geom_edge_link(aes(width = weight), alpha = 0.8) + 
  scale_edge_width(range = c(0.2, 2)) +
  geom_node_text(aes(label = name), repel = TRUE) +
  labs(edge_width = "Correlation") +
  theme_graph()
